Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Guideline for International Students

### 2024-01-25 demystify.tex
Updates from Overleaf

\section{Interview}

Many PhD programs have the tradition of interviewing applicants. The most common case is that a professor is interested in working with a student and so want to chat with them to make decision (e.g., to offer them RA).
In some case, the interview is done by several professors, e.g., to see if a student fits to their group or to recruit a very strong student to their program.

Typically, an interview takes about 15-30 minutes, and one important aspect of evaluation is your ability to effectively communicate, including speaking and understanding English. A professor might want to know more about your research background or even ask you to read a paper (so be sure to do it!). Finally, during the interview, you will have the opportunity to ask questions about the university. It's essential to prepare some thoughtful questions, similar to a job interview.

In short, getting an interview is a good sign; it means that someone is considering you. If they are not interested in your application, they will not proceed with an interview.
However, do not worry much if you do not get an interview! For example, at GMU, most of our admitted students with TA do not go through any interviews.

>>>>

\section{Interview}
Sometimes a faculty wants to interview an applicant to make a decision. Typically, this means that they are considering admitting you. If they are not interested in your application, they will not proceed with an interview.

Typically, an interview takes about 15-30 minutes, and one important aspect of evaluation is your ability to effectively communicate, including speaking and understanding English. In addition, during the interview, you will have the opportunity to ask questions about the university. It's essential to prepare some thoughtful questions, similar to a job interview.
